Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-23 paper-v1.tex
fix redundant meets
fix token symbol typo

\section{Background}
\subsection{Peer-review: present problems and mild solutions}
Peer review is still the only quality control mechanism devoted to evaluate scientific outcomes. The purpose of peer review is "improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism." \cite{Gropp-PeerRevStress}. However, the system is 'ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues, here reviewed.
\paragraph{A slow multi-stage process.} The main issues affecting the effectiveness of peer-review is the delay between paper submission and journal acceptance for publication. The traditional peer-review process is completely controlled by the editor(s). The author(s) submit manuscript to the journal where an editorial team assesses if the paper meets meets the scopes of the journal and novelty criteria. If the editorial decision is to send the manuscript for review, the handling editor personally selects potential reviewers. The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves (single-blind review). Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript and sometimes substantially improving the draft. If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers. The same reviewers might be contacted again and if they want they can follow up the peer-review process. This process can take multiple rounds and is a huge time investment both for authors and reviewers. An analysis of all papers published in PubMed for a time period of 30 years claims that the median review time is around 100 days\cite{Kendall-peerrev}.
\paragraph{Lack of recognition.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the 'impact factor' of an author). Thus, it does not lead to advancements in career or help securing grants. Researchers are motivated in doing peer-review for a sense of belonging and a desire to 'give back' to the community. A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation or let bad science being published through sloppy and uncritical reviews.
\paragraph{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud. Some studies have reported an improvement in the transparency and 'civility; of the review process when open reports are released according to the standards of open peer review.
\paragraph{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination, social prestige of the institution. To solve this problem some journals have implemented double-blind review process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
\paragraph{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?".
\paragraph{Need for more reviewers.} There is a disproportion between the progressive increase in journals publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists. \cite{tragedy-reviewers}.

@@

\begin{enumerate}
    \item \textbf{Ants-Review process - scenario 1 (journal-dependent)}: The author submits a manuscript to the journal. If the papers passes the stages of editorial decision (appropriateness of style and coherence with the journal's scope). The editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract. The bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal. Reviews fulfilling the smart-contract requirements are validated by the journal editors and voted via QV. When the reviews are accepted (\emph{bounty fulfillment}), reviewers are awarded a token called \emph{ANT}.
    \item \textbf{Ants-Review process - scenario 2 (community-driven)}: The author submits a manuscript to the pre-print service or to an hypothetical Ants-Review platform. The paper is accepted by the community for revision in its whatever format. The author issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract. The bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker. Reviews fulfilling the smart-contract requirements are validated by the Ants-Review community of contributors. When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}. Reviews will be voted by the community via Quadratic Voting.In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty. Since it is in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit and therefore will fuel ethical behaviour.

>>>>

\section{Background}
\subsection{Peer-review: present problems and mild solutions}
Peer review is still the only quality control mechanism devoted to evaluate scientific outcomes. The purpose of peer review is "improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism." \cite{Gropp-PeerRevStress}. However, the system is 'ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues, here reviewed.
\paragraph{A slow multi-stage process.} The main issues affecting the effectiveness of peer-review is the delay between paper submission and journal acceptance for publication. The traditional peer-review process is completely controlled by the editor(s). The author(s) submit manuscript to the journal where an editorial team assesses if the paper meets the scopes of the journal and novelty criteria. If the editorial decision is to send the manuscript for review, the handling editor personally selects potential reviewers. The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves (single-blind review). Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript and sometimes substantially improving the draft. If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers. The same reviewers might be contacted again and if they want they can follow up the peer-review process. This process can take multiple rounds and is a huge time investment both for authors and reviewers. An analysis of all papers published in PubMed for a time period of 30 years claims that the median review time is around 100 days\cite{Kendall-peerrev}.
\paragraph{Lack of recognition.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the 'impact factor' of an author). Thus, it does not lead to advancements in career or help securing grants. Researchers are motivated in doing peer-review for a sense of belonging and a desire to 'give back' to the community. A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation or let bad science being published through sloppy and uncritical reviews.
\paragraph{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud. Some studies have reported an improvement in the transparency and 'civility; of the review process when open reports are released according to the standards of open peer review.
\paragraph{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination, social prestige of the institution. To solve this problem some journals have implemented double-blind review process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
\paragraph{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?".
\paragraph{Need for more reviewers.} There is a disproportion between the progressive increase in journals publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists. \cite{tragedy-reviewers}.

@@

\begin{enumerate}
    \item \textbf{Ants-Review process - scenario 1 (journal-dependent)}: The author submits a manuscript to the journal. If the papers passes the stages of editorial decision (appropriateness of style and coherence with the journal's scope). The editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract. The bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal. Reviews fulfilling the smart-contract requirements are validated by the journal editors and voted via QV. When the reviews are accepted (\emph{bounty fulfillment}), reviewers are awarded a token called \emph{ANTS}.
    \item \textbf{Ants-Review process - scenario 2 (community-driven)}: The author submits a manuscript to the pre-print service or to an hypothetical Ants-Review platform. The paper is accepted by the community for revision in its whatever format. The author issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract. The bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker. Reviews fulfilling the smart-contract requirements are validated by the Ants-Review community of contributors. When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANTS}. Reviews will be voted by the community via Quadratic Voting.In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty. Since it is in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit and therefore will fuel ethical behaviour.
